### 2016-09-07 Theorem3_FP.tex

\acnote{To be verified before moving the theorem to section 4}
\heading{Classical Bloom filter in random oracle model (ROM). }
As discussed earlier, the classical Bloom filter (BF) is an instantiation of a set multiplicity data structure and admits errors in form of false  positives (FP) only. In the ROM, $\Rep$ queries the random oracle to get the hash indices of elements of set $S$. It then computes the $m$-bit array, $M$ and outputs $\privaux=\emptystring$, $\pubaux = \emptystring$ and $M$ as the representation of
the Bloom filter. The $\Qry$ oracle uses the random oracle in a similar way. For any query $q$, it gets the hash indices $h_1, \ldots, h_k$ from the random oracle and returns 1 if $M[h_i(x)]=1$ for all $i\in [k]$, and 0 otherwise.
\begin{theorem}\label{thm3}
Fix $k,m,n,r>0$. Let $A$ be an adaptive adversary (for attacking BF) asking $q$ queries to the random oracle. Let $t$ be the running time of $A$ given these queries. Then, 
\[
\AdvCorrect{{BF},\distr{\calS}{},r}{A} \leq  {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}

\begin{proof}[\Cref{thm3}]
The proof of this theorem will follow along the lines of \Cref{thm2}.
\end{proof}

>>>>

\acnote{INCOMPLETE. To be verified before moving the theorem to section 4}
\heading{Classical Bloom filter in random oracle model (ROM). }
Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).  The following result shows,
\begin{theorem}\label{thm3}
Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described. For any adversary~$A$ that makes a total of~$q$ queries to the oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}

\begin{proof}[\Cref{thm3}]
We use a game playing argument to prove this theorem in the ROM. In $\game{0}$, the $\HashOracle$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO). For every distinct query, $\Hash$ returns a random value sampled from $[m]$. Here, the adversary $A$, along with $\Rep$ and $\Qry$ are given access to $\Hash$. It can be seen that, $\game{0}$ exactly simulates the correctness game of $\Pi_{\mathrm{Bloom}}$. So, $\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A) = 1}$.

\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(q_x)$}\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
if $a \neq q_x(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\
%
\oracle{$\HashOracle(i,q_y)$}\\
$v \getsr [m]$\\
if $T[i,q_y] \neq \undefined$\\
\nudge $v \gets T[i,q_y]$\\
$T[i,q_y] \gets v$\\
Ret $v$
}
{
\underline{$\game{1}(A)$}\\
$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\ 
%
\oracle{$\TestOracle(q_x)$}\\
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j,q_x)$\\
\nudge if $M[h_j] \neq 1$ then Return $(0, \err)$\\
$\err \gets \err +1$\\
Return~$(1,\err )$\\
%
\oracle{$\HashOracle(i,q_y)$}\\
$v \getsr [m]$\\
if $T[i,q_y] \neq \undefined$\\
\nudge $v \gets T[i,q_y]$\\
$T[i,q_y] \gets v$\\
Ret $v$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{$\game{2}(A)$}\\
$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\ 
%
\oracle{$\TestOracle(q_x)$}\\
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j,q_x)$\\
\nudge if $M[h_j] \neq 1$\\
\nudge \nudge if $j = 1$ then Return $(0, \err, \emptystring)$\\
\nudge \nudge Return $(0, \err, (h_1, \ldots, h_{j-1}))$\\
$\err \gets \err +1$\\
Return~$(1,\err, (h_1, \ldots, h_{k}) )$\\
%
\oracle{$\HashOracle(i,q_y)$}\\
$v \getsr [m]$\\
if $T[i,q_y] \neq \undefined$\\
\nudge $v \gets T[i,q_y]$\\
$T[i,q_y] \gets v$\\
Ret $v$
}
{
\underline{$\game{3}(A)$}\\
$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\ 
%
\oracle{$\TestOracle(q_x)$}\\
$M \gets\pubaux $\\
$(h_1, \ldots, h_{k}) \gets \HashOracle(q_x)$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $M[h_j] \neq 1$ then \\
\nudge \nudge Return~$(0,\err, (h_1, \ldots, h_{k}) )$\\
$\err \gets \err +1$\\
Return~$(1,\err, (h_1, \ldots, h_{k}) )$\\
%
\oracle{$\HashOracle(q_y)$}\\
$v_j \getsr [m]$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $T[j,q_y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,q_y]$\\
\nudge $T[j,q_y] \gets v_j$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm3}: Game playing argument}\label{fig:3TGame}
\end{figure}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{4}(A)\fbox{\game{5}(A)}}\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$, $\Ans \gets \emptyset$\\
$c \gets 0$, $\bad \gets \false$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(q_x)$}\\
if $\Ans[x] \neq \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(q_x)$\\
Return $\Ans[x]$\\
%
}
{
\oracle{$\HashOracle(q_y)$}\\
$c \gets c + 1$\\
$v_j \getsr [m]$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $T[j,x] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,q_y]$\\
\nudge $T[j,q_y] \gets h_j$\\
%
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $M[v_j] \neq 1$ then \\
\nudge \nudge $\Ans[q_y] \gets (0,\err, (v_1, \ldots, v_{k}) )$\\
\nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge \nudge $\Break$\\
if $c \notin \calI$ then $\bad \gets \true$\\
$\err \gets \err +1$\\
$\Ans[q_y] \gets (0,\err, (v_1, \ldots, v_{k}))$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm3}: Game playing argument}\label{fig:3TGame}
\end{figure}

%The proof of this theorem will follow along the lines of \Cref{thm2}. As in previous proofs, we use a game playing argument to prove this theorem as well. In $\game{0}$, the $\HashOracle$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO). It can be observed that, $\game{0}$ exactly simulates the BF's correctness game attacked by an adaptive adversary. So, $\AdvCorrect{{BF},\distr{\calS}{},r}{A} = \Prob{\game{0}(A) = 1}$.
%
%In $\game{1}$, assuming $A$ does not make any pointless queries, $\HashOracle$ is modified to sample random elements from $[m]$. In addition, $\Test$ sets $\bad$ to $\true$ if queries indexed by set $\calI$ fail to be FPs, or if any of the remaining queries are FPs. $\game{2}$, on the other hand is exactly same as $\game{1}$ except it returns 0, if $\bad$ is set to $\true$. It can be easily seen that, $\game{1}$ and $\game{2}$ are exactly same as $\game{2}$ and $\game{3}$ of \Cref{thm2}'s game playing argument. So, 
%\begin{align*}
%\Prob{\game{1}(A)=1} = \Prob{\game{0}(A)=1}\\
%\Prob{\game{2}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{1}(A)=1}
%\end{align*}
%\Cref{fig:D} shows non-adaptive adversary, $D$ that finds $r$ FPs against the standard BF. Using a similar explanation from previous proofs,
%\begin{align*}
%\AdvCorrect{{BF},\distr{\calS}{},r}{D} &= \Prob{\game{2}(A) = 1}\\
%\AdvCorrect{{BF},\distr{\calS}{},r}{D} &\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \,.
%\end{align*}
%To summarize, we have
%\[
%\AdvCorrect{{BF},\distr{\calS}{},r}{A} \leq  {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
%\]

\end{proof}

### 2016-09-07 syntax.tex

\heading{Preliminaries. } When~$\univ$ is a set and $n>0$ is an
integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets
of~$\univ$, and $[[\univ]]^n$ for the set of all multisets
over~$\univ$ with total multiplicity~$n$. \tsnote{We may not need all
  of that.} We write $x \getsr \univ$ to denote
sampling an element from~$\univ$ and assigning this to~$x$, and we
extend this notation to randomized algorithms.  When~$X$ is a string
over some alphabet~$\Sigma$, we write $|X|$ for the bitlength
of~$X$, relative to some fixed encoding.  When~$X$ is a multiset, we
overload the notation so that~$|X|$ is the total multiplicity of~$X$.

Algorithms may be provided black-box access to one or more oracles, which we write as superscripts, e.g., $F^{O_1,O_2,\ldots}$.  An \emph{adversary} is a randomized algorithm

\heading{Data structures.}  We begin by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset.
%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$, and a set of multisets~$\calS$ over
$\univ$. 
A \emph{data structure} (for $\calS$) is a tuple $\setprim=(\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
\item $\Rep \colon \mathcal{S} \to \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
    \emph{public representation data} $\pubaux \in \bits^*$ and
    \emph{private representation data} $\privaux \in \bits^*$. We write
    $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
\item $\Qry\colon \Sigma^* \times \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $\pubaux,\privaux \in
    \bits^*$ and $q \in \calQ$, and outputting
    an \emph{answer} $a \in \Gamma$.  We write $a \gets
    \Qry(\pubaux,\privaux,q)$ for this execution.
\end{itemize}
\hfill\dqed
\end{definition}

@@

\begin{definition}[Error probability and rate] \rm
Fix a data structure $\setprim=(\calQ,\Rep, \Qry)$. Let $\mathrm{Err}(S,q,\pubaux,\privaux)$ be a predicate that is
true iff $\Qry(\pubaux,\privaux, q) \neq q(S)$.  Then a data structure
has \emph{error probability} $\epsilon$ if
$\max_{S,q}\Pr[(\pubaux,\privaux) \getsr \Rep(S) :
\mathrm{Err}(S,q,\pubaux,\privaux)=1 ] \leq \epsilon$.
%
It has \emph{error rate} $\tilde{\epsilon}$ if
$\max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, q \getsr \calQ :
\mathrm{Err}(S,q,\pubaux,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
\end{definition}

\noindent The definition can be lifted to the random-oracle model by
giving $\Rep, \Qry$ access to a random oracle. In that case, the
probabilities defining the error probability and error rate are also
taken over choice of the random oracle.

@@

\def\bin{{\sf Bin}}
\heading{``Trivial'' attacks, and error probability vs.\ error rate. }
Let~$\Pi$ be a scheme that is $(1-\epsilon)$-correct, and consider
an attack that asks random queries $q_1,q_2,\ldots,q_T$, i.e.,
uniform samples from~$\calQ$.
Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(\pubaux,\privaux,q_i)\neq q_i(S)$.
The $(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability that $\mathrm{Err}_i=1$ is at most~$\epsilon$,
and it is tempting to model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials with success probability~$\epsilon$.
However, a moment's reflection shows that this is not the case.  Concretely, consider the following scheme.  Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$.  For the queries, let $\calQ = \{q_x\colon \calS \to \bits \,|\, \forall x \in \univ\}$ where $\forall S \in \calS$ the predicate $q_x(S)=1 \Leftrightarrow x \in S$.  Let $\Rep(S)$ pick a random element~$s \in S$, and return $M = S \setminus \{s\}$ and $\privaux = \emptystring$.  To respond to queries, let~$\Qry(\pubaux,\privaux,q_x)=1$ iff $x \in M$.  It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error, and the remaining $|\univ|-n$ queries have probability zero of causing an error.  Moreover, once the coins of~$\Rep$ are fixed, there is exactly \emph{one} query that will cause an error.  Thus for random queries from~$Q$, for all~$i\in[T]$ we have $\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.

@@

\heading{Data Structures for Set-Multiplicity Queries. } Our particular focus
will be on data structures that support multiplicity queries, of
which set-membership queries are a special case.
\begin{definition} A \emph{set-multiplicity data structure} is a data
structure with $\Gamma=\mathbb{N}$ and
where $\calQ=\{q_x \,|\, x \in \univ\}$ where $q_x(S)$ is defined to
be the multiplicity of~$x$ in the multiset~$S$. \hfill\dqed
\end{definition}

It is not hard to see Bloom filters are an instantiation of a
set-multiplicity data structure.  Fix $\Sigma=\Gamma=\bits$.  Define
algorithm~$\Rep$, with functions $k=k(|S|), m=m(|S|)$ and a
description of a hash function family~$\mathcal{H}=\{h \colon \univ
\to \{1,2,\ldots,m\}\}$ hardwired into it, to sample hash functions
$h_1, \ldots, h_k$ from~$\mathcal{H}$ and then compute an $m$-bit
array~$M$ (intialized to 0 everywhere) by setting $M[h_i(x)]=1$ for
all $i\in [k]$ and $x \in S$.  Finally, $\Rep$ returns
$\privaux=\emptystring$ and $\pubaux = M$ as the
representation.
%
The algorithm~$\Qry$ is defined so that, on input $(\pubaux,\privaux,q_x)$, it
returns the minimum of the values $M[h_1(x)],\ldots,M[h_k(x)]$.  We note that, while our error
probability and error rate do not distinguish among ``types'' of
errors, they also do not preclude instantiations (like the classical
Bloom filter) that admit only one type of error, e.g.
false-positives.

As a simple extension, consider $\Sigma=\mathbb{N}$ and modify the
basic Bloom filter so that it stores counters, rather than
bits, at each position in an array.  In particular, for each~$x \in
S$ the $\Rep$~algorithm increments the counters stored at positions
$h_1(x), h_2(x), \ldots, h_k(x)$, returns the final array of
counters as~$M$.  The $\Qry$-algorithm remains the same. Such a
construction gives a static version of a counting Bloom
filter~\cite{xxx}.  We will capture dynamic versions, as well as
count-min sketches~\cite{xxx}, scalable Bloom filters~\cite{xxx},
etc., in a later section.\tsnote{If we ultimately do!}

@@

By setting $\Sigma=\bits^L$ for a specified $L>0$, we capture the
so-called ``garbled Bloom filter'' due to Dong, Chen and
Wen~\cite{xxx}.  This stores xor-shares of bitstring~$x \in S$ at
positions $h_1(x),h_2(x),\ldots,h_k(x)$ in an array.  Similarly, the
cuckoo-hashing construction from NY, which (loosely speaking) stores a
hash $g(x)$ at positions determined by $h_1(x),h_2(x),\ldots,h_k(x)$,
is captured when $L=|g(x)|$. \tsnote{Check the correctness of this claim.}

>>>>

\heading{Preliminaries. } When~$\univ$ is a set and $n>0$ is an
integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets
of~$\univ$, and $[[\univ]]^n$ for the set of all multisets
over~$\univ$ with total multiplicity~$n$. \jnote{I guess we are
viewing sets as a special case of multisets, so maybe just say
that.} \tsnote{We may not need all
  of that.} We write $x \getsr \univ$ to denote
sampling an element uniformly from~$\univ$ and assigning it to~$x$,
and we extend this notation to randomized algorithms. When~$X$ is a
string over some alphabet~$\Sigma$, we write $|X|$ for the bitlength
of~$X$, relative to some fixed encoding.  When~$X$ is a multiset, we
overload the notation so that~$|X|$ is the total multiplicity
of~$X$.

Algorithms may be provided black-box access to one or more oracles,
which we write as superscripts, e.g., $F^{O_1,O_2,\ldots}$.  An \emph{adversary} is a randomized algorithm.

\heading{Data structures.}  We begin by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset.
%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$, and a collection of (multi)sets~$\calS$
over $\univ$. A \emph{data structure} (for $\calS$) is a tuple
$\setprim=(\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
\item $\Rep \colon \mathcal{S} \to \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input a (multi)set $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
    \emph{public representation data} $\pubaux \in \bits^*$ and
    \emph{private representation data} $\privaux \in \bits^*$. We write
    $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
\item $\Qry\colon \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $\pubaux,\privaux \in \bits^*$
    and a query $q \in \calQ$, and outputting an \emph{answer}
    $a \in \Gamma$.  We write $a \gets \Qry(\pubaux,\privaux,q)$
    for this execution.
\end{itemize}
\hfill\dqed
\end{definition}

@@

\begin{definition}[Error probability and rate] \rm
For a given data structure $\setprim=(\calQ,\Rep, \Qry)$, let
$\mathrm{Err}(S,q,\pubaux,\privaux)$ be a predicate that is true iff
$\Qry(\pubaux,\privaux, q) \neq q(S)$.  Then $\Pi$ has \emph{error
probability} $\epsilon$ if $\max_{S,q}\Pr[(\pubaux,\privaux) \getsr
\Rep(S) : \mathrm{Err}(S,q,\pubaux,\privaux)=1 ] \leq \epsilon$.
%
It has \emph{error rate} $\tilde{\epsilon}$ if
$\max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, q \getsr \calQ :
\mathrm{Err}(S,q,\pubaux,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
\end{definition}

\noindent The definitions above can be lifted to the random-oracle
model by giving $\Rep, \Qry$ access to a random oracle. In that
case, the probabilities defining the error probability and error
rate are also taken over choice of the random oracle.

@@

We note that, while our error probability and error rate do not
distinguish among ``types'' of errors, they also do not preclude
instantiations (like the classical Bloom filter) that admit only one
type of error, e.g., false positives.

\def\bin{{\sf Bin}}
\heading{``Trivial'' attacks, and error probability vs.\ error
rate.} \jnote{Not sure this belongs here. I'd rather move any
discussion of ``attacks'' (trivial or not) to later. But if we just
want to highlight the difference between error and error rate we
could do that here.} Let~$\Pi$ be a scheme that is
$(1-\epsilon)$-correct, and consider an attack that asks random
queries $q_1,q_2,\ldots,q_T$, i.e., uniform samples from~$\calQ$.
Let $\mathrm{Err}_i$ be a random variable indicating the event
$\Qry(\pubaux,\privaux,q_i)\neq q_i(S)$. The
$(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability
that $\mathrm{Err}_i=1$ is at most~$\epsilon$, and it is tempting to
model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials with success
probability~$\epsilon$. However, a moment's reflection shows that
this is not the case.  Concretely, consider the following scheme.
Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$. For the
queries, let $\calQ = \{q_x\colon \calS \to \bits \,|\, \forall x
\in \univ\}$ where $\forall S \in \calS$ the predicate $q_x(S)=1
\Leftrightarrow x \in S$.  Let $\Rep(S)$ pick a random element~$s
\in S$, and return $M = S \setminus \{s\}$ and $\privaux =
\emptystring$.  To respond to queries,
let~$\Qry(\pubaux,\privaux,q_x)=1$ iff $x \in M$.  It is easy to see
that this scheme is $1/n$-correct; for any fixed~$S$, there are
exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the
coins of~$\Rep$) of causing a correctness error, and the remaining
$|\univ|-n$ queries have probability zero of causing an error.
Moreover, once the coins of~$\Rep$ are fixed, there is exactly
\emph{one} query that will cause an error.  Thus for random queries
from~$Q$, for all~$i\in[T]$ we have
$\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.

@@

\heading{Data structures for set-multiplicity queries.} Our
particular focus will be on data structures that support
multiplicity queries, of which set-membership queries are a special
case.
\begin{definition} \rm
A \emph{set-multiplicity data structure} is a data structure with
$\Gamma=\mathbb{N}$ and $\calQ=\{q_x\}_{x \in \univ}$, where
$q_x(S)$ is defined to be the multiplicity of~$x$ in the
multiset~$S$. \hfill\dqed
\end{definition}

We illustrate our notation by casting Bloom filters as a particular
example of a set-multiplicity data structure. \jnote{Only handles
sets, not multisets.} Let $\Gamma=\bits$, and fix functions
$k(\cdot)$ and $m(\cdot)$ parameterizing the scheme. Algorithm
$\Rep$, on input a set~$S$, computes $k=k(|S|)$ and $m=m(|S|)$ and
then chooses $k$ functions $h_1, \ldots, h_k \in \mathcal{H}$ for
some function family $\mathcal{H}=\{h \colon \univ \to
\{1,2,\ldots,m\}\}$. \jnote{Note depends on $m$. It might be easier
(especially since we talk about error) to already let the hash
functions be independent random oracles.} It then computes an
$m$-bit array~$M$ (initialized to 0 everywhere) by setting
$M[h_i(x)]=1$ for all $i\in [k]$ and $x \in S$.  Finally, $\Rep$
returns $\privaux=\emptystring$ and $\pubaux = M$ as the
representation.
%
Algorithm~$\Qry$ is defined so that, on input
$(\pubaux,\privaux,q_x)$, it returns the minimum of the values
$M[h_1(x)],\ldots,M[h_k(x)]$. \jnote{How does $\Qry$ know the hash
functions?}

As a simple extension, consider $\Gamma=\mathbb{N}$ and modify the
basic Bloom filter so that it stores counters, rather than bits, at
each position in an array.  In particular, for each~$x \in S$ the
$\Rep$~algorithm increments the counters stored at positions
$h_1(x), h_2(x), \ldots, h_k(x)$, returns the final array of
counters as~$M$.  The $\Qry$-algorithm remains the same. Such a
construction gives a static version of a counting Bloom
filter~\cite{xxx}.  We will capture dynamic versions, as well as
count-min sketches~\cite{xxx}, scalable Bloom filters~\cite{xxx},
etc., in a later section.\tsnote{If we ultimately do!}

@@

By setting $\Sigma=\bits^L$ for a specified $L>0$, we can capture
the so-called ``garbled Bloom filter'' due to Dong, Chen and
Wen~\cite{xxx}. \jnote{Details have to be filled in.} This stores
xor-shares of bitstring~$x \in S$ at positions
$h_1(x),h_2(x),\ldots,h_k(x)$ in an array. Similarly, the
cuckoo-hashing construction from NY, which (loosely speaking) stores
a hash $g(x)$ at positions determined by
$h_1(x),h_2(x),\ldots,h_k(x)$, is captured when $L=|g(x)|$.
\tsnote{Check the correctness of this claim.}
